Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-19 tex/sections/consensus.tex
Clarify the analysis of emergency forking
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The reserve committee does not know the value of $h_{\max}$. However, if the reserve committee creates all fork blocks
with heights~$h_0,h_0+1,h_0+2,\dots$ every fork block with height $h \geq h_{\max} + 2$ will surely get a certificate.
If there is no block in the main chain with height~$h_{\max} + 1$, then the fork block with height~$h_{\max} +
1$ will also get a certificate, otherwise the reserve committee should be able to eventually find the main block
at $h_{\max}+1$ and generate a fork block with height~$h_{\max} + 2$ as its successor. This way, the reserve
committee will always be able to create at least one fork block which gets certified and continue the chain after the
fork block with the highest height.

@@

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block whose parent is block $b_2$, that will essentially discard $b_1$. Notice
that if a block at height $h+1$ had been certified by validators the fork block after $b_2$ could not have received a
certificate from validators.

>>>>

The reserve committee must be able to create at least one fork block which gets a certificate from validators.
The reserve committee may not know the value of $h_{\max}$.\footnote{This could happen when the network is
partitioned.} However, if the reserve committee creates all fork blocks
with heights~$h_0,h_0+1,h_0+2,\dots$ for some $h_0 \leq h_{\max} + 2$,
then every fork block with height~$h \geq h_{\max} +
2$ will surely get a certificate. Obviously $h_v \leq h_{\max}$, so if the main chain contains a block with height
$h_{\max} + 1$ the reserve committee should be able to eventually find this block and generate the fork block with
height $h_{\max} + 2$, which will surely get a certificate.
If there is no block in the main chain with height~$h_{\max} + 1$, then the fork block with
height~$h_{\max} + 1$ can get a certificate. This way, the reserve committee will always be able to continue the chain
after the certified fork block with the highest height.

@@

During the emergency forking, no more than one block with a validators certificate can be discarded. A fork block
with height~$h+1$ can not receive a certificate without a certified normal parent block with
height~$h$ or $h-1$, or another certified fork block with height~$h$.

One certified block may be discarded when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ with heights
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block whose parent is block $b_2$, and that will essentially discard $b_1$. Notice
that if a block at height $h+1$ had been certified by validators the fork block after $b_2$ could not have received a
certificate from validators.
